Classical density functional theory for the square-well liquid

### 2015-08-05 papers/square-well-fluid/paper.tex
add caption for sw coexistence plot (and update SConstruct which was broken) Tested on darcy. Took 0:52.08.
new SW homogeneous plots and add TODO for SW stuff Tested on darcy. Took 1:29.47.
add reference to nice review of modern monte carlo methods Tested on darcy. Took 0:51.98.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/coexistence-ww1_3}
\end{center}
\caption{Pressure.}
\label{fig:coexistencec}
\end{figure}

@@

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/coexistence-ww1_3}
\end{center}
\caption{Liquid-vapor coexistence curve for the square-well fluid as
  predicted using thermodynamic perturbation theory.}
\label{fig:coexistencec}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/free-energy-vs-eta}
\end{center}
\caption{Free energy.}
\label{fig:free-energy-vs-eta}
\end{figure}

@@

\section{EXTRA}

Here is a nice review article that introduces numerous modern Monte
Carlo methods for fluids~\cite{dubbeldam2013inner}.
